The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor edits to paper

\begin{document}
\title{The  \emph{FThresholds} package for \emph{Macaulay2}}
%\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
%\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
%\email{fernanal@post.bgu.ac.il}
%\thanks{A.F.\,Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}

@@

%\author[]{Zhibek Kadyrsizova}
%\address{School of Science and Technology, Nazarbayev University, Astana, 010000, Republic of Kazakhstan}
%\email{zhibek.kadyrsizova@nu.edu.kz}
%\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}

@@

%\author[]{Daniel Smolkin}
%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
%\email{smolkin@math.utah.edu}
%\thanks{D.~Smolkin was supported by NSF RTG Grant DMS \#1246989, NSF CAREER Grant DMS \#1252860/1501102, and NSF FRG Grant DMS \#1265261/1501115.}

@@

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
\end{abstract}

\subjclass[2010]{13A35}%=

@@

\maketitle

>>>>

\newenvironment{nouppercase}{%
  \let\uppercase\relax%
  \renewcommand{\uppercasenonmath}[1]{}}{}

\begin{document}
\title{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}

@@

@@

@@

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
\end{abstract}

\subjclass[2010]{13A35}

@@

\begin{nouppercase}
\maketitle
\end{nouppercase}
